---
title: "Northeast Natural History Conference"
output: html_notebook
---

R code for generating figure about camera trap data accumulation for 2023 presenation at Northeaset Natural History Conference, co-authored with Brett Ford.

Goal: Illustrate the huge amount of data genereated by camera trapping that needs to be managed.

Set things up
```{r}
rm(list = ls())
library(tidyverse)
library(here)

```

Now pull in data
```{r}
pics<-read.csv(here("Data", "picture_data.csv"))
```

This data set is a rough approximation of all of the camera trapping images I have collected since 2019, for demonstration purposes only. There may be a little bit of duplication in counting, and there may be images that have not been counted.

Let's summarise to plot

```{r}
pic_summary<-pics %>% group_by(Year) %>% summarise(
  num_photos = sum(Photos)
)
```
Now create a cumulative column
```{r}
pic_summary<- pic_summary %>% mutate(
  cum_photos = cumsum(num_photos)
)
```
Great!

Now plot

```{r}
ggplot(pic_summary, aes(Year, cum_photos))+
  geom_point(size = 4)+
  geom_line(size = 1.5)+
 expand_limits(y = c(55000, 95000))+
  scale_y_continuous(labels = scales::comma)+ #prevents scientific notation
  labs(y = "Cumulative number of photos")+
  theme(
    axis.text = element_text(size = 12, color = "black"),
    axis.title = element_text(size = 14, color = "black")
    )
```
Now save file

```{r}
ggsave(here("Data", "pics_over_time.png"), width = 6, height = 4)
```


